\documentclass[prodmode]{acmlarge}

\pdfpagewidth=8.5in
\pdfpageheight=11in


\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{bbding}
\usepackage{pifont}
\usepackage[T1]{fontenc}
\usepackage{pslatex}
\usepackage{url}
%\usepackage{minted}
\usepackage{listings}



\acmVolume{}
\acmNumber{}
\acmArticle{}
\articleSeq{}
\acmYear{2013}
\acmMonth{10}

\markboth{Bijvank et al.}{Software Architecture Patterns for System Administration Support}
\title{Software Architecture Patterns for System Administration Support}
\author{ROLAND BIJVANK \affil{HU University of Applied Sciences, Utrecht, the Netherlands}\ \\
WIEBE WIERSEMA \affil{HU University of Applied Sciences, Utrecht, the Netherlands}\ \\
CHRISTIAN K\"{O}PPE \affil{HAN University of Applied Sciences, Arnhem, the Netherlands}}
\parskip=0.3em

\begin{abstract}
Many quality aspects of software systems are addressed in the existing literature on software architecture patterns. But the aspect of system administration seems to be a bit overlooked, even though it is an important aspect too.

In this work we present three software architecture patterns that, when applied by software architects, support the work of system administrators: {\sc Provide an Administration API}, {\sc Single File Location}, and {\sc Centralized System Logging}. {\sc Provide an Administration API} should solve problems encountered when trying to automate administration tasks. The {\sc Single File Location} pattern should help system administrators to find the files of an application in one (hierarchical) place. {\sc Centralized System Logging} is useful to prevent coming up with several logging formats and locations.

\end{abstract}

\category{D.2.11}{Software Engineering}{Software Architectures}[(Design) Patterns]
%\category{D.4.3}{Operating Systems}{File Systems Management}{File organization}
%\category{D.2.10}{Software Engineering}{Design}[Design Patterns]
%\category{K.3.2}{Computers and Education}{Computer and Information Science Education }[Computer science education]

\terms{Software Architecture, System Administration}
\keywords{Software Architecture, System Administration}
\acmformat{Bijvank, R., Wiersema, W., K\"{o}ppe, C. 2013. Software Architecture Patterns for System Administration Support}
%\copyr{PLoP'13, October 23-21, Tucson, Arizona, USA. Copyright 2012 is held by the author(s). ACM xxx}
\copyr{}

\begin{document}
\begin{bottomstuff}
Authors' addresses: roland.bijvank@hu.nl; wiebe.wiersema@hu.nl; christian.koppe@han.nl\\
Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. To copy otherwise, to republish, to post on servers or to redistribute to lists, requires prior specific permission. A preliminary version of this paper was presented in a writers' workshop at the 20th Conference on Pattern Languages of Programs (PLoP). PLoP'13, October 23-26, Monticello, Illinois, USA. Copyright 2013 is held by the author(s). ISBN todo
\end{bottomstuff}


\maketitle

% This will be the definitive version of this paper for the ACM Library! Remarks and comments have been added to the ultimate version of the paper.

\input{introduction}
\input{patternformat}

\include{patterns/provideAPI}
\include{patterns/singleFileLocation}
\include{patterns/systemLogging}

\input{conclusion}

\section{Acknowledgements}
We wish to express many thanks to our shepherd Eduardo Guerra for all his useful comments and feedback. Furthermore the feedback given by the participants of the writers' workshop at the PLoP'13 conference helped a lot to improve this work.

%\bibliographystyle{plain}
% Referentie naar Poort en Vliet dienen nog uit de bibliografie verwijderd te worden.
\bibliographystyle{acmlarge}
\bibliography{ArchitecturePatterns}
\end{document}
