\newpage
\section*{PROVIDE AN ADMINISTRATION API}

%The system has to offer the possibility of different administration possibilities, as e.g. a regular %performance check, creation of a new user or a re-start in the case of problems, but also the signalling of a %critical condition. 
The system has to provide an API (application programming interface) that allows the system administrator to automate system administration tasks. Examples of such tasks are: a regular performance check, creation of a new user or a re-start in the case of problems, but also the signaling of a critical condition.  

\begin{center}
\ding{118} \ding{118} \ding{118}
\end{center}

\textbf{If the administrative interface is a GUI, many of the standard administration tasks can not be automated. Repetitive tasks have to be completed again and again, which leads to a high frustration of the administrators. It also can be hard to get remote access to such a GUI.}\\

\textit{Unexpected usage.} System administrators have their own ways of organizing their administration tasks. The strive to automate many parts, often in unexpected ways, and a GUI is minimizing the possibilities of doing so.\\

\textit{Admin OS vs. System OS.} The operating systems which admins are using for their administration tasks often differ from the OS the application to be administered is running on. Providing a GUI as administrative interface often means that this GUI is only executable on certain OS's, which certainly restricts system administrators in an unnecessary way.

\begin{center}
\ding{118} \ding{118} \ding{118} 
\end{center}

\textbf{Therefore: Provide an API for all required administration functionality. Make this API available, easily accessible and well documented, so that admins can automate administrative tasks and integrate it easily in the administration processes.}\\

Offering an API for the administrator provides much more flexibility to the system administrators for administering the systems in the way they think fits best. It gives them enough freedom to integrate the administration in existing processes.

Tools for automation can make use of the administration functionality if they can connect to the provided API. The right API helps to automate tasks that are part of a new employee account creation process. \cite{Limoncelli2011a}.

\begin{center}
\ding{118} \ding{118} \ding{118} 
\end{center}

\textit{Rationale.}\\
Using this pattern will make the life of a system administrator more pleasant, especially in cross-platform situations, as it removes the platform-specific issues caused by a graphical administration interface. In combination with a cross-platform scripting language (e.g. Python, Ruby, TCL) this pattern shows its real strength as one can uniformly approach the administration API on any given platform.

